cardinalR: Generating interesting high-dimensional data structures

### 2025-10-05 paper-cardinalR.Rmd
Updated Table 6

```{r}
pyramid_tb <- tibble(fun = c("gen_pyrrect",
                             "gen_pyrtri",
                             "gen_pyrstar",
                             "gen_pyrfrac"), 
                        exp = c("Rectangular-base pyramid, with a sharp or blunted apex.",
          "Triangular-base pyramid, with a sharp or blunted apex.",
          "Star-shaped base pyramid, with a sharp or blunted apex.",
          "Pyramid containing triangular pyramid-shaped holes."))
```

>>>>

```{r}
pyramid_tb <- tibble(fun = c("gen_pyrrect",
                             "gen_pyrtri",
                             "gen_pyrstar",
                             "gen_pyrfrac"), 
                        exp = c("Rectangular-base, with a sharp or blunted apex.",
          "Triangular-base, with a sharp or blunted apex.",
          "Star-shaped base, with a sharp or blunted apex.",
          "Pyramid with triangular pyramid-shaped holes."))
```

### 2025-10-05 paper-cardinalR.tex
Remove linear projections
Updated Table 6

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/linear-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `linear` data.}\label{fig:linear-proj}
\end{figure}

@@

\caption{\label{tab:pyramid-tb-pdf}cardinalR pyramid data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_pyrrect & Rectangular-base pyramid, with a sharp or blunted apex.\\
gen\_pyrtri & Triangular-base pyramid, with a sharp or blunted apex.\\
gen\_pyrstar & Star-shaped base pyramid, with a sharp or blunted apex.\\
gen\_pyrfrac & Pyramid containing triangular pyramid-shaped holes.\\
\bottomrule
\end{tabular}
\end{table}

>>>>

@@

\caption{\label{tab:pyramid-tb-pdf}cardinalR pyramid data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_pyrrect & Rectangular-base, with a sharp or blunted apex.\\
gen\_pyrtri & Triangular-base, with a sharp or blunted apex.\\
gen\_pyrstar & Star-shaped base, with a sharp or blunted apex.\\
gen\_pyrfrac & Pyramid with triangular pyramid-shaped holes.\\
\bottomrule
\end{tabular}
\end{table}
